Alexis Roche

### 2020-01-13 cv/cv.tex
Nouveau texte pour chanson de Tom

\newcommand{\bighead}[3]{\noindent\begin{minipage}{.85\textwidth}{\bf #1}\newline {\bf #2}\end{minipage}\begin{minipage}{.15\textwidth}\begin{flushright}{\bf #3}\end{flushright}\end{minipage}\newline\noindent\rule{.85\textwidth}{0.4pt}}

\newcommand{\head}[2]{{\noindent {\bf #1} $\mid$ {\bf #2}}}

@@

\begin{flushright} 
{\huge {\bf Alexis Roche}}\\
\begin{small}
+351 910 327 756 $\mid$ \url{alexis.roche@gmail.com}\\
\url{https://www.linkedin.com/in/alexis-roche-3815592}\\
French National $\mid$ DOB 12/8/1972 $\mid$ Married, 2 Children\\
\end{small}
\end{flushright}

@@

\noindent Senior-level engineer and applied researcher with a specialist expertise in computer vision, medical image analysis and machine learning, operating in the fields of applied research, health industry and domestic appliance industry. Graduated from the French ``Grande \'Ecole" CentraleSupelec, and holder of a PhD. Strong experience in developing research and commercial software.

\noindent {\em Keywords:} image processing, statistics, machine learning, structural and functional brain magnetic resonance imaging, Python.

@@

\noindent {\bf DATA SCIENCE:} In-depth knowledge of statistics, computer vision, medical image analysis, traditional machine learning and deep learning.

\ \\
\noindent {\bf NEUROIMAGING:} Extensive experience in developing algorithms for structural and functional brain magnetic resonance imaging (MRI) in the form of open-source and commercial software for neuroscience, clinical research \& clinical practice.

\ \\
\noindent {\bf SCIENTIFIC COMPUTING:} Over ten years experience in Python programming using the NumPy/SciPy ecosystem and interfacing C~language with Python.

\ \\
\noindent {\bf INTERACTION:} Proven ability to work in multidisciplinary environments at the interface of industry and academic research, as well as to develop successful collaborations with physicians and fundamental life science researchers.

\ \\
\noindent {\bf SCIENTIFIC WRITING:} Main author of 25 peer-reviewed scientific articles published in international journals, proceedings and books, co-author of more than 100 scholarly publications and 5 international patents.

@@

\bighead{SENIOR COMPUTER VISION SCIENTIST}{CoVii, Ar\c celik/Beko group, Porto, Portugal}{2017--present}
\begin{itemize}
\item Developing object recognition and tracking algorithms for smart domestic appliances (VUXHub and Artisan applications demonstrated at IFA Berlin, 2017).
\end{itemize}

\ \\
\bighead{LEAD CLINICAL RESEARCH -- ADVANCED CLINICAL IMAGING TECHNOLOGY}{Siemens Healthineers / Lausanne University Hospital (CHUV), Switzerland}{2011--2017}
\begin{itemize}
\item Led algorithmic development of the {\em MorphoBox} Siemens prototype for brain morphometry using anatomical MRI to help radiological reading for patients with suspected neurodegeneration.
\item Contributed a number of clinical validation studies of brain morphometry in collaboration with neurologists and radiologists, via statistical analysis and data mining techniques, in Alzheimer's disease and other dementia, mild cognitive impairment, multiple sclerosis, migraine, anorexia, \ldots 
\item Co-supervised three PhD students and two MSc students.
\item Main organizer of annual Siemens/CHUV {\em brain imaging} workshops in Lausanne, Switzerland, 2012--2016.
\end{itemize}

\ \\
\bighead{PERMANENT RESEARCHER -- NEUROIMAGING INSTITUTE}{French Atomic Commission (CEA), Paris, France}{2002--2011}
\begin{itemize}
\item Developed advanced algorithms for image processing and statistical analysis of functional, anatomical and diffusion-weighted MRI data (population analysis, spatio-temporal image registration, real-time imaging).
\item French ANR-funded project management: PI (Karametria project, statistical analysis of brain structures, budget: 620 K\euro, 2009--2011), team leader (NIBB project, studying language in infants via functional neuroimaging, 2006--2009).
\item Active contributor to the NiPy software library (Neuroimaging in Python, \url{www.nipy.org}) from 2006.
\item Main supervisor of two PhD students and four MSc students.
\item Worked as Academic Guest at Computer Vision Laboratory, Swiss Federal Institute of Technology Zurich (ETHZ), Switzerland, 2009--2011, on brain image registration. 
\end{itemize}

\ \\
\bighead{RESEARCH ASSISTANT -- WOLFSON MEDICAL VISION LABORATORY}{University of Oxford, UK}{2001--2002}
\begin{itemize}
\item Developed advanced medical image registration algorithms.
\item Consulting work for Mirada Solutions Ltd (now Siemens Molecular Imaging) on image-based deformation tracking (brain, liver).
\end{itemize}

\ \\
\bighead{CONTINGENT SCIENTIST -- FRENCH NATIONAL SERVICE}{General Directorate for Armament (DGA), Vernon, France}{1996--1997}
\begin{itemize}
\item Developed plane trajectory simulator using stochastic process models.
\end{itemize}

\heading{Education}

\head{PhD, Engineering Science (1997--2001)}{University of Nice-Sophia Antipolis, France}
\begin{itemize}
\item Funded by French National Research Institute (INRIA), Sophia Antipolis unit.
\item Developed generic algorithm for multimodal image registration, with applications in radiotherapy, image-guided surgery and neuroscience.
\end{itemize}

\ \\
\head{MSc, Cognitive Science (1995--1996)}{University Pierre \& Marie Curie, Paris \rom{6}, France}
\begin{itemize}
\item Internship at Experimental Psychology Laboratory, National Center for Scientific Research (CNRS), Paris, France, on modeling human perception of tempo using artificial neural networks.
\end{itemize}

\ \\
\head{Engineer Degree (equivalent MSc) (1993--1996)}{Ecole Centrale Paris (now CentraleSupelec), France}
\begin{itemize}
\item Third year specialization in Applied Mathematics.
\end{itemize}

@@

\heading{Additional information}

\noindent 
\begin{minipage}{.15\textwidth}
{\bf Languages:}
\end{minipage}
\begin{minipage}{.85\textwidth}
Native French, fluent English, basic Italian \& Portuguese. %German.
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
{\bf Programming:}
\ \\ 
\ \\
\ \\ 
\ \\
\ \\ 
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} C/C++ \\
{\tiny$\bullet$} Python (numpy, scipy, pylab, sklearn, TensorFlow, keras, nipy, cython)\\ 
{\tiny$\bullet$} Matlab\\
{\tiny$\bullet$} R. \\
{\tiny$\bullet$} Version control software (git, svn).\\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
{\bf Publications:}
\ \\ 
\ \\
\  \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} Over 100 scholarly publications. \\
{\tiny$\bullet$} Google scholar statistics: 9146 citations, h-index: 31, i10-index: 57 (December 2018).\\
{\tiny$\bullet$} International patents: 4 published + 1 pending application \\
\end{minipage}

%\ \\
%\noindent 
%\begin{minipage}{.15\textwidth}
%{\bf Reviewing:}
%\ \\ 
%\ \\
%\end{minipage}
%\begin{minipage}{.85\textwidth}
%IEEE Transactions on Medical Imaging, Medical Image Analysis, NeuroImage, Frontiers in
% Neuroscience, IEEE Transactions on Image Processing, Signal Image and Video Processing, MICCAI conference, \ldots
%\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
{\bf Teaching:}
\ \\ 
\ \\
\  \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} Brain morphometry post-graduate lecture (2h), Lausanne: UNIL (2014/16), EPFL (2015/16).\\
{\tiny$\bullet$} Statistical analysis in neuroimaging, INSERM/CNRS continuing education, France (10h/year from 2003 to 2015).\\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
{\bf References:}
\end{minipage}
\begin{minipage}{.85\textwidth}
Available on request.
\end{minipage}

>>>>

\newcommand{\bighead}[3]{\noindent\begin{minipage}{.85\textwidth}{\textbf{#1}}\newline {\textbf{#2}}\end{minipage}\begin{minipage}{.15\textwidth}\begin{flushright}{\textbf{#3}}\end{flushright}\end{minipage}\newline\noindent\rule{.85\textwidth}{0.4pt}}

\newcommand{\head}[2]{{\noindent {\textbf{#1}} $\mid$ {\textbf{#2}}}}

@@

\begin{flushright} 
{\huge {\textbf{Alexis Roche}}}\\
\begin{small}
+351 910 327 756 $\mid$ \url{alexis.roche@gmail.com}\\
\url{https://www.linkedin.com/in/alexis-roche-3815592}\\
French National $\mid$ DOB 12/8/1972 $\mid$ Married, 2 Children\\
\end{small}
\end{flushright}

@@

\noindent Senior-level engineer and applied researcher with a specialist expertise in computer vision, medical image analysis and machine learning, operating in the fields of applied research, healthcare, electro-domestic and entertainment industry. Graduated from the French ``Grande \'Ecole" CentraleSupelec (formely, Centrale Paris), and holder of a PhD. Strong experience in developing research and commercial software. {\em Keywords:} artificial intelligence, image processing, computer vision, machine learning, deep learning, statistics, brain imaging, Python.

@@

\noindent \textbf{DATA SCIENCE:} In-depth knowledge of statistics, computer vision, medical image analysis, traditional machine learning and deep learning.

\ \\
\noindent \textbf{NEUROIMAGING:} Extensive experience in developing algorithms for structural and functional brain magnetic resonance imaging (MRI) in the form of open-source and commercial software for neuroscience, clinical research \& clinical practice.

\ \\
\noindent \textbf{SCIENTIFIC COMPUTING:} Over ten years experience in Python programming using the NumPy/SciPy ecosystem and interfacing C~language with Python.

\ \\
\noindent \textbf{INTERACTION:} Proven ability to work in multidisciplinary environments at the interface of industry and academic research, as well as to develop successful collaborations with physicians and fundamental life science researchers.

\ \\
\noindent \textbf{SCIENTIFIC WRITING:} Main author of 25 peer-reviewed scientific articles published in international journals, proceedings and books, co-author of more than 100 scholarly publications and 5 international patents.

@@

\bighead{SENIOR COMPUTER VISION ENGINEER}{Didimo, Porto, Portugal}{2019--present}
\nopagebreak
\begin{itemize}
\item Developing computer vision algorithms for high-fidelity 3D avatars.
\end{itemize}
\ \\

\bighead{SENIOR COMPUTER VISION SCIENTIST}{CoVii, Ar\c celik/Beko group, Porto, Portugal}{2017--2019}
\nopagebreak
\begin{itemize}
\item Developed embedded object recognition and tracking algorithms for smart domestic appliances using traditional computer vision and deep learning (VUXHub and Artisan applications demonstrated at IFA Berlin, 2017--18).
\end{itemize}

\ \\
\bighead{LEAD CLINICAL RESEARCH -- ADVANCED CLINICAL IMAGING TECHNOLOGY}{Siemens Healthineers / Lausanne University Hospital (CHUV), Switzerland}{2011--2017}
\nopagebreak
\begin{itemize}
\item Led algorithmic development of the {\em MorphoBox} Siemens prototype for brain morphometry using anatomical MRI to help radiological reading for patients with suspected neurodegeneration.
\item Contributed a number of clinical validation studies of brain morphometry in collaboration with neurologists and radiologists, via statistical analysis and data mining techniques, in Alzheimer's disease and other dementia, mild cognitive impairment, multiple sclerosis, migraine, anorexia, \ldots 
\item Co-supervised three PhD students and two MSc students.
\item Main organizer of annual Siemens/CHUV {\em brain imaging} workshops in Lausanne, Switzerland, 2012--2016.
\end{itemize}

\ \\
\bighead{PERMANENT RESEARCHER -- NEUROIMAGING INSTITUTE}{French Atomic Commission (CEA), Paris, France}{2002--2011}
\nopagebreak
\begin{itemize}
\item Developed advanced algorithms for image processing and statistical analysis of functional, anatomical and diffusion-weighted MRI data (population analysis, spatio-temporal image registration, real-time imaging).
\item French ANR-funded project management: PI (Karametria project, statistical analysis of brain structures, budget: 620 K\euro, 2009--2011), team leader (NIBB project, studying language in infants via functional neuroimaging, 2006--2009).
\item Active contributor to the NiPy software library (Neuroimaging in Python, \url{www.nipy.org}) from 2006.
\item Main supervisor of two PhD students and four MSc students.
\item Worked as Academic Guest at Computer Vision Laboratory, Swiss Federal Institute of Technology Zurich (ETHZ), Switzerland, 2009--2011, on brain image registration. 
\end{itemize}

\ \\
\bighead{RESEARCH ASSISTANT -- WOLFSON MEDICAL VISION LABORATORY}{University of Oxford, UK}{2001--2002}
\nopagebreak
\begin{itemize}
\item Developed advanced medical image registration algorithms.
\item Consulting work for Mirada Solutions Ltd (now Siemens Molecular Imaging) on image-based deformation tracking (brain, liver).
\end{itemize}

\ \\
\bighead{CONTINGENT SCIENTIST -- FRENCH NATIONAL SERVICE}{General Directorate for Armament (DGA), Vernon, France}{1996--1997}
\nopagebreak
\begin{itemize}
\item Developed plane trajectory simulator using stochastic process models.
\end{itemize}

\heading{Education}
\nopagebreak
\head{PhD, Engineering Science (1997--2001)}{University of Nice-Sophia Antipolis, France}
\begin{itemize}
\item Funded by French National Research Institute (INRIA), Sophia Antipolis unit.
\item Developed generic algorithm for multimodal image registration, with applications in radiotherapy, image-guided surgery and neuroscience.
\end{itemize}

\ \\
\head{MSc, Cognitive Science (1995--1996)}{University Pierre \& Marie Curie, Paris \rom{6}, France}
\nopagebreak
\begin{itemize}
\item Internship at Experimental Psychology Laboratory, National Center for Scientific Research (CNRS), Paris, France, on modeling human perception of tempo using artificial neural networks.
\end{itemize}

\ \\
\head{Engineer Degree (equivalent MSc) (1993--1996)}{Ecole Centrale Paris (now CentraleSupelec), France}
\nopagebreak
\begin{itemize}
\item Third year specialization in Applied Mathematics.
\end{itemize}

@@

\heading{Additional information}
\nopagebreak
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Languages:}
\end{minipage}
\begin{minipage}{.85\textwidth}
Native French, fluent English, basic Italian \& Portuguese. %German.
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Programming:}
\ \\ 
\ \\
\ \\ 
\ \\
\ \\ 
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} C/C++ \\
{\tiny$\bullet$} Python (numpy, scipy, pylab, skimage, opencv, sklearn, TensorFlow, keras, cython...)\\ 
{\tiny$\bullet$} Matlab\\
{\tiny$\bullet$} R. \\
{\tiny$\bullet$} Version control software (git, svn).\\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 5754 citations, h-index: 32, i10-index: 56 (September 2019).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}

%\ \\
%\noindent 
%\begin{minipage}{.15\textwidth}
%\textbf{ Reviewing:}
%\ \\ 
%\ \\
%\end{minipage}
%\begin{minipage}{.85\textwidth}
%IEEE Transactions on Medical Imaging, Medical Image Analysis, NeuroImage, Frontiers in
% Neuroscience, IEEE Transactions on Image Processing, Signal Image and Video Processing, MICCAI conference, \ldots
%\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Teaching:}
\ \\ 
\ \\
\  \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} Brain morphometry post-graduate lecture (2h), Lausanne: UNIL (2014/16), EPFL (2015/16).\\
{\tiny$\bullet$} Statistical analysis in neuroimaging, INSERM/CNRS continuing education, France (10h/year from 2003 to 2015).\\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{References:}
\end{minipage}
\begin{minipage}{.85\textwidth}
Available on request.
\end{minipage}
